{{< var titll >}}

### 2024-07-11 paper.qmd
abc

@@

# {{< var sec3.nmn >}}
## {{< var sec3.un1 >}}
## {{< var sec3.un2 >}}

@@

# {{< var sec6.nmn >}}
## {{< var sec6.un1 >}}
## {{< var sec6.un2 >}}
## {{< var sec6.un3 >}}
## {{< var sec6.un4 >}}

@@

```{r, echo=FALSE, results='asis',warning=F}
#presm <- paste0(rprojroot::find_rstudio_root_file(), '/presentation.qmd')
#textm <- readLines(presm)
#cat(knitr::knit_child(text = paste(textm[25:length(textm)], collapse = "\n"), quiet = TRUE))
```

>>>>

```{r}
library(ManifoldDestiny)
library(huxtable)
library(kableExtra)
source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/simulations.R'))
```

@@

# {{< var sec3.nmn >}}

## {{< var sec3.un1 >}}
```{r}
#| echo: false
#| output: false
apps <- basc
```
{{< include tab.qmd >}}

## {{< var sec3.un2 >}}
### Normal form
```{r}
#| echo: false
#| output: false
apps <- rigv[[1]]
```
{{< include tab.qmd >}}

### Hybrid
```{r}
#| echo: false
#| output: false
apps <- rigv[[2]]
```
{{< include tab.qmd >}}

### Opposition
```{r}
#| echo: false
#| output: false
apps <- rigv[[3]]
```
{{< include tab.qmd >}}

@@

# {{< var sec6.nmn >}}

## {{< var sec6.un1 >}}
```{r}
#| echo: false
#| output: false
apps <- ManifoldDestiny::app1
```
{{< include tab.qmd >}}

## {{< var sec6.un2 >}}
```{r}
#| echo: false
#| output: false
apps <- ManifoldDestiny::app2
```
{{< include tab.qmd >}}

## {{< var sec6.un3 >}}
```{r}
#| echo: false
#| output: false
apps <- ManifoldDestiny::app2
```
{{< include tab.qmd >}}

## {{< var sec6.un4 >}}
```{r}
#| echo: false
#| output: false
apps <- ManifoldDestiny::app4
```
{{< include tab.qmd >}}

@@

### 2024-07-11 tab.qmd
abc

---
title: ""
params:
  name: "0"
---

```{r, echo=T}
params$name
```

```{r, echo=F,message=FALSE,warning=FALSE}
#| echo: false
#| output: false
#| message: false
sw <- as.numeric(params$name)
if(sw == 0) {
ManifoldDestiny::wasmconload()
library(ManifoldDestiny)
source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmconverting.R"))
source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmnonverting.R"))
source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/simulations.R'))
source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/applications.R'))
apps <- ManifoldDestiny::app0
}
```

>>>>

```{r, echo=F,message=FALSE,warning=FALSE}
#| echo: false
#| output: false
#| message: false
params <- list(name="0")
sw <- as.numeric(params$name)
if(sw == 0) {
ManifoldDestiny::wasmconload()
library(ManifoldDestiny)
source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmconverting.R"))
source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmnonverting.R"))
source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/simulations.R'))
source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/applications.R'))
apps <- ManifoldDestiny::app0
}
```
